Fusion Moves for Correlation Clustering

### 2014-11-07 paper/anytimefigure2.tex
new plots

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pgfplotsset{every axis legend/.append style={
at={(1.0,1.2)},
anchor=north east}} 
\begin{figure*}[p]
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  restrict y to domain=0:4620,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  %ymin =  75282844.25,
  %ymax =  81774642.015,
  %xtick       = { 1 , 60 , 3600 },
  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
  %ytick       = {75661636, 78718140, 81774643 },
  %yticklabels = {$75661636$, $78718140$, $81774643$ },
  width = 1.0\columnwidth,
  scaled ticks = false,
  ]
  %\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-150.data};
  %\addlegendentry{HC-CGC}

  \addplot[color=red,mark=x] table[x=time,y=CGC-planar]{data2/image-seg.data};
  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data2/image-seg.data};
  \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC]{data2/image-seg.data};
 % \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data2/image-seg.data};
  \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-MC]{data2/image-seg.data};
  \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data2/image-seg.data};

  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{image-seg}
  \end{subfigure}
  \begin{subfigure}[b]{0.33\textwidth}
    \centering
    \begin{tikzpicture}
    \begin{semilogxaxis}[
    restrict y to domain=-6000:-4400,
    xlabel = {runtime},
    xmin = 0,
    xmax = 4100,
    %ymin =  75282844.25,
    %ymax =  81774642.015,
    %xtick       = { 1 , 60 , 3600 },
    %xticklabels = { 1 sec. , 1 min.  , 1 hour },
    %ytick       = {75661636, 78718140, 81774643 },
    %yticklabels = {$75661636$, $78718140$, $81774643$ },
    width = 1.0\columnwidth,
    scaled ticks = false
    ]
    %\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data2/knott-3d-150.data};
    %%\addlegendentry{HC-CGC}
    %
    \addplot[color=red,mark=x] table[x=time,y=CGC]{data2/knott-3d-150.data};            
    \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data2/knott-3d-150.data};
    \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC]{data2/knott-3d-150.data};  
    \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data2/knott-3d-150.data}; 
    \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-CGC]{data2/knott-3d-150.data};
    \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data2/knott-3d-150.data};

    \end{semilogxaxis}
    \end{tikzpicture}
    \caption{knott-3d-150}
  \end{subfigure}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  restrict y to domain=-40000:-24000,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  %ymin =  75282844.25,
  %ymax =  81774642.015,
  %xtick       = { 1 , 60 , 3600 },
  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
  %ytick       = {75661636, 78718140, 81774643 },
  %yticklabels = {$75661636$, $78718140$, $81774643$ },
  width = 1.0\columnwidth,
  scaled ticks = false,
  legend to name = named,
  legend columns=5
  ]
  \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data2/knott-3d-300.data};          \addlegendentry{HC-CGC}
  \addplot[color=red,mark=x] table[x=time,y=CGC]{data2/knott-3d-300.data};               \addlegendentry{CGC}
  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data2/knott-3d-300.data};       \addlegendentry{MC-I}
  \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC]{data2/knott-3d-300.data};    \addlegendentry{Fusion-HC-MC}
  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data2/knott-3d-300.data};    \addlegendentry{Fusion-HC-CGC}
  \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-CGC]{data2/knott-3d-300.data};  \addlegendentry{Fusion-WS-CGC}
  \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data2/knott-3d-300.data};          \addlegendentry{KL}

  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{knott-3d-300}
  \end{subfigure}
  \newline
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  restrict y to domain=-80000:-60000,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  %ymin =  75282844.25,
  %ymax =  81774642.015,
  %xtick       = { 1 , 60 , 3600 },
  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
  %ytick       = {75661636, 78718140, 81774643 },
  %yticklabels = {$75661636$, $78718140$, $81774643$ },
  width = 1.0\columnwidth,
  scaled ticks = false
  ]
  \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data2/knott-3d-450.data};
  \addplot[color=red,mark=x] table[x=time,y=CGC]{data2/knott-3d-450.data};
  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data2/knott-3d-450.data};
  \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC]{data2/knott-3d-450.data};
  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data2/knott-3d-450.data};
  \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-CGC]{data2/knott-3d-450.data};
  \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data2/knott-3d-450.data};

  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{knott-3d-450}
  \end{subfigure}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  restrict y to domain=-10000000:-100000,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  %ymin =  75282844.25,
  %ymax =  81774642.015,
  %xtick       = { 1 , 60 , 3600 },
  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
  %ytick       = {75661636, 78718140, 81774643 },
  %yticklabels = {$75661636$, $78718140$, $81774643$ },
  width = 1.0\columnwidth,
  scaled ticks = false
  ]
  \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data2/knott-3d-550.data};
  \addplot[color=red,mark=x] table[x=time,y=CGC]{data2/knott-3d-550.data};
  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data2/knott-3d-550.data};
  \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC]{data2/knott-3d-550.data};
  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data2/knott-3d-550.data};
  \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-CGC]{data2/knott-3d-550.data};
  \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data2/knott-3d-550.data};

  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{knott-3d-550}
  \end{subfigure}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\begin{subfigure}[H]
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  %restrict y to domain=-10000000:-100000,
  %restrict y to domain=-10000000:1200000,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  %ymin =  75282844.25,
  %ymax =  81774642.015,
  %xtick       = { 1 , 60 , 3600 },
  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
  %ytick       = {75661636, 78718140, 81774643 },
  %yticklabels = {$75661636$, $78718140$, $81774643$ },
  width = 1.0\columnwidth,
  scaled ticks = false
  ]
  \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data2/seg-3d.data};
  \addplot[color=red,mark=x] table[x=time,y=CGC]{data2/seg-3d.data};
  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data2/seg-3d.data};
  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC]{data2/seg-3d.data}; 
  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data2/seg-3d.data}; 
  \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-CGC]{data2/seg-3d.data};
  \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data2/seg-3d.data};

  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{seg-3d}
  \end{subfigure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  %restrict y to domain=-10000000:-100000,
  %restrict y to domain=-10000000:100000,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  %ymin =  75282844.25,
  %ymax =  81774642.015,
  %xtick       = { 1 , 60 , 3600 },
  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
  %ytick       = {75661636, 78718140, 81774643 },
  %yticklabels = {$75661636$, $78718140$, $81774643$ },
  width = 1.0\columnwidth,
  scaled ticks = false
  ]
  \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data2/socialnets.data};
  \addplot[color=red,mark=x] table[x=time,y=CGC]{data2/socialnets.data};
  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data2/socialnets.data};
  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC]{data2/socialnets.data};
  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data2/socialnets.data};
  \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-CGC]{data2/socialnets.data};

  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{social nets}
  \end{subfigure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  %restrict y to domain=-10000000:-100000,
  %restrict y to domain=-10000000:100000,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  %ymin =  75282844.25,
  %ymax =  81774642.015,
  %xtick       = { 1 , 60 , 3600 },
  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
  %ytick       = {75661636, 78718140, 81774643 },
  %yticklabels = {$75661636$, $78718140$, $81774643$ },
  width = 1.0\columnwidth,
  scaled ticks = false
  ]
  \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data2/normalizedsocialnets.data};
  \addplot[color=red,mark=x] table[x=time,y=CGC]{data2/normalizedsocialnets.data};
  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data2/normalizedsocialnets.data};
  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC]{data2/normalizedsocialnets.data};
  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data2/normalizedsocialnets.data};
  \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-CGC]{data2/normalizedsocialnets.data};

  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{social nets}
  \end{subfigure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  %restrict y to domain=-10000000:-100000,
  %restrict y to domain=-10000000:100000,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  %ymin =  75282844.25,
  %ymax =  81774642.015,
  %xtick       = { 1 , 60 , 3600 },
  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
  %ytick       = {75661636, 78718140, 81774643 },
  %yticklabels = {$75661636$, $78718140$, $81774643$ },
  width = 1.0\columnwidth,
  scaled ticks = false
  ]
  \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data2/modularity-clustering.data};
  \addplot[color=red,mark=x] table[x=time,y=CGC]{data2/modularity-clustering.data};
  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data2/modularity-clustering.data};
  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC]{data2/modularity-clustering.data};
  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data2/modularity-clustering.data};
  \addplot[color=orange,mark=x] table[x=time, y=DYNCC-HC-CGC]{data2/modularity-clustering.data};
  \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data2/modularity-clustering.data};

  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{modularity clustering}
  \end{subfigure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pgfplotsset{every axis legend/.append style={
at={(1.0,1.2)},
anchor=north east}} 
\begin{figure*}[p]
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  restrict y to domain=0:4620,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  width = 1.0\columnwidth,
  scaled ticks = false,
  every axis legend/.code={\let\addlegendentry\relax} 
  ]  
  \anytimeplot{image-seg}
  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{image-seg}
  \end{subfigure}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
  \begin{subfigure}[b]{0.33\textwidth}
    \centering
    \begin{tikzpicture}
    \begin{semilogxaxis}[
    restrict y to domain=-6000:-4400,
    xlabel = {runtime},
    xmin = 0,
    xmax = 4100,
    width = 1.0\columnwidth,
    scaled ticks = false,
    every axis legend/.code={\let\addlegendentry\relax} 
    ] 
    \anytimeplot{knott-3d-150}

    \end{semilogxaxis}
    \end{tikzpicture}
    \caption{knott-3d-150}
  \end{subfigure}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  restrict y to domain=-40000:-24000,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  width = 1.0\columnwidth,
  scaled ticks = false,
  legend to name = named,
  legend columns=6
  ]  
  \anytimeplot{knott-3d-300}
  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{knott-3d-300}
  \end{subfigure}
  \newline
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  restrict y to domain=-80000:-60000,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  width = 1.0\columnwidth,
  scaled ticks = false,
  every axis legend/.code={\let\addlegendentry\relax} 
  ] 
  \anytimeplot{knott-3d-450} 
  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{knott-3d-450}
  \end{subfigure}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  restrict y to domain=-10000000:-100000,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  width = 1.0\columnwidth,
  scaled ticks = false,
  every axis legend/.code={\let\addlegendentry\relax} 
  ]
  \anytimeplot{knott-3d-550} 
  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{knott-3d-550}
  \end{subfigure}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\begin{subfigure}[H]
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  %restrict y to domain=-10000000:-100000,
  %restrict y to domain=-10000000:1200000,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  width = 1.0\columnwidth,
  scaled ticks = false,
  every axis legend/.code={\let\addlegendentry\relax} 
  ] 
  \anytimeplot{seg-3d} 
  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{seg-3d}
  \end{subfigure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  %restrict y to domain=-10000000:-100000,
  %restrict y to domain=-10000000:100000,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  width = 1.0\columnwidth,
  scaled ticks = false,
  every axis legend/.code={\let\addlegendentry\relax} 
  ] 
  \anytimeplot{socialnets} 
  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{social nets}
  \end{subfigure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  %restrict y to domain=-10000000:-100000,
  %restrict y to domain=-10000000:100000,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  width = 1.0\columnwidth,
  scaled ticks = false,
  every axis legend/.code={\let\addlegendentry\relax} 
  ]
  \anytimeplot{normalizedsocialnets}
  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{normalized social nets}
  \end{subfigure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  %restrict y to domain=-10000000:-100000,
  %restrict y to domain=-10000000:100000,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  width = 1.0\columnwidth,
  scaled ticks = false,
  every axis legend/.code={\let\addlegendentry\relax} 
  ] 
  \anytimeplot{modularity-clustering}
  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{modularity clustering}
  \end{subfigure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2014-11-07 paper/egpaper_for_review.tex
new plots

@@

>>>>

% \newcommand{\anytimeplot}[1]{
%   \addplot[color=brown,mark=x] table[x=time,y=HC]{data3/knott-3d-300.data};              \addlegendentry{HC}
%   \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data3/knott-3d-300.data};          \addlegendentry{HC-CGC}
%   \addplot[color=red,mark=x] table[x=time,y=CGC]{data3/knott-3d-300.data};               \addlegendentry{CGC}
%   \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data3/knott-3d-300.data};          \addlegendentry{KL}
%   \addplot[color=purple,mark=x] table[x=time, y=MCR-CCFDB]{data3/knott-3d-300.data};     \addlegendentry{MC-R}
%   \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data3/knott-3d-300.data};       \addlegendentry{MC-I}
%   \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC]{data3/knott-3d-300.data};    \addlegendentry{Fusion-HC-MC}
%   \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data3/knott-3d-300.data};    \addlegendentry{Fusion-HC-CGC}
%   \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-MC]{data3/knott-3d-300.data};  \addlegendentry{Fusion-WS-MC}
%   \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-CGC]{data3/knott-3d-300.data};  \addlegendentry{Fusion-WS-CGC}
% }
\newcommand{\anytimeplot}[1]{
  \addplot[color=brown,mark=x] table[x=time,y=HC]{data3/#1.data};              \addlegendentry{HC}
  \addplot[color=black,mark=square] table[x=time,y=HC-CGC]{data3/#1.data};          \addlegendentry{HC-CGC}
  \addplot[color=red,mark=x] table[x=time,y=CGC]{data3/#1.data};               \addlegendentry{CGC}
  \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data3/#1.data};          \addlegendentry{KL}
  \addplot[color=purple,mark=o] table[x=time, y=MCR-CCFDB]{data3/#1.data};     \addlegendentry{MC-R}
  \addplot[color=blue,mark=o] table[x=time, y=MCI-CCIFD]{data3/#1.data};       \addlegendentry{MC-I}
  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC]{data3/#1.data};    \addlegendentry{Fusion-HC-MC}
  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data3/#1.data};    \addlegendentry{Fusion-HC-CGC}
  \addplot[color=orange,mark=o] table[x=time, y=DYNCC-WS-MC]{data3/#1.data};  \addlegendentry{Fusion-WS-MC}
  \addplot[color=pink,mark=x] table[x=time, y=DYNCC-WS-CGC]{data3/#1.data};  \addlegendentry{Fusion-WS-CGC}
}

@@

\input{anytimefigure2.tex}
